Using Fundamental Measure Theory to treat the Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2013-08-08 papers/pair-correlation/paper.tex
Modified the alternate path plot and the paper to use it and to annotate the x-axis nicely in pair-correlation. This is a temporary change, as the annotation is done in the paper and will need to be separate. Also fixed a small bug in triplet-monte-carlo.cpp. Tested everything on paho-deb.

\documentclass[letterpaper,twocolumn,amsmath,amssymb,pre]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-1.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-1}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-2.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-2}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-3.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-3}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-4.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-4}
\end{figure}

>>>>

\documentclass[letterpaper,twocolumn,amsmath,amssymb,pre]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{color}
\usepackage{tikz}
\usetikzlibrary{arrows,decorations.pathreplacing}

@@

\begin{figure}
  \begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-alt-1.pdf}};
    \draw [decorate, decoration = {brace, mirror, raise=0.5cm}]
    (4.75, .75) node(a){} -- (5.95, .75) node(b){};
    \draw [decorate, decoration = {brace, mirror, raise=0.5cm}]
    (5.99, .75) node(a){} -- (7.83, .75) node(b){};
  \end{tikzpicture}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-1}
\end{figure}

\begin{figure}
  \begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-alt-2.pdf}};
    \draw [decorate, decoration = {brace, mirror, raise=0.5cm}]
    (4.75, .75) node(a){} -- (5.95, .75) node(b){};
    \draw [decorate, decoration = {brace, mirror, raise=0.5cm}]
    (5.99, .75) node(a){} -- (7.83, .75) node(b){};
  \end{tikzpicture}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-2}
\end{figure}
\begin{figure}
  \begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-alt-3.pdf}};
    \draw [decorate, decoration = {brace, mirror, raise=0.5cm}]
    (4.75, .75) node(a){} -- (5.95, .75) node(b){};
    \draw [decorate, decoration = {brace, mirror, raise=0.5cm}]
    (5.99, .75) node(a){} -- (7.83, .75) node(b){};
  \end{tikzpicture}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-3}
\end{figure}
\begin{figure}
  \begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=\columnwidth]{figs/pair-correlation-pretty-alt-4.pdf}};
    \draw [decorate, decoration = {brace, mirror, raise=0.5cm}]
    (4.75, .75) node(a){} -- (5.95, .75) node(b){};
    \draw [decorate, decoration = {brace, mirror, raise=0.5cm}]
    (5.99, .75) node(a){} -- (7.83, .75) node(b){};
  \end{tikzpicture}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:pair-distribution-4}
\end{figure}
